Optimal updating factor in adaptive flat-distribution-sampling simulations

### 2016-06-09 doc/invt.tex
fix a scanave.py bug
invt.tex: add table of symbols

\documentclass[preprint, floatfix]{revtex4-1}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{upgreek}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{hyperref}
\usepackage{setspace}

@@

\definecolor{DarkBlue}{RGB}{0,0,64}
\definecolor{DarkBrown}{RGB}{64,20,10}
\definecolor{DarkGreen}{RGB}{0,64,0}
\definecolor{DarkPurple}{RGB}{64,0,42}
% annotation macros
\newcommand{\repl}[2]{{\color{gray} [#1] }{\color{blue} #2}}
\newcommand{\add}[1]{{\color{blue} #1}}
\newcommand{\del}[1]{{\color{gray} [#1]}}
\newcommand{\note}[1]{{\color{DarkGreen}\footnotesize \textsc{Note.} #1}}
\newcommand{\answer}[1]{{\color{DarkBlue}\footnotesize \textsc{Answer.} #1}}
\newcommand{\summary}[1]{{\color{DarkPurple}\footnotesize \textsc{Summary.} #1}}

@@

Diagonalizing the matrix $\mathbf w$
using the eigenvectors defined in Eqs.
\eqref{eq:eig_w}-\eqref{eq:eig_orthonormal_rows},
we get a set of decoupled equations
%
\begin{equation}
  \dot y_k(t)
  =
  -\alpha(t) \, \lambda_k \, [y_k(t) - \theta_k(t)],
\label{eq:yt_diffeq}
\end{equation}
%
where
\begin{align}
  y_k(t)
  &=
  \sum_{j=1}^n
    \phi_{kj} \, x_j(t)
  ,
  \label{eq:y_def}
  \\
  \theta_k(t)
  &=
  \sum_{j=1}^n
    \phi_{kj} \, \xi_j(t)
  .
  \label{eq:eta_def}
\end{align}

@@

\begin{figure}[h]
\begin{center}
  \makebox[\linewidth][c]{
    \includegraphics[angle=0, width=1.0\linewidth]{fig/erriascan.pdf}
  }
  \caption{
    \label{fig:erriascan}
    Relative error
    versus the initial updating magnitude, $\alpha(0)$,
    for optimal schedules with different $q(T)$.
    Assuming the Gaussian updating scheme
    with $\sigma = 10$,
    and $\alpha_0 = 10^{-4}$.
    %
    The points were obtained from averaging results
    from 1000 independent simulations;
    the curves are theoretical predictions.
    %
    \note{This figure was produced by
      \texttt{doc/fig/erriascan.gp}.
      The data were saved under
      \texttt{data/iascan}.
    }%
  }
\end{center}
\end{figure}

@@

First, if the sampling is perfect,
%Eq. \eqref{eq:kappa_delta} is exact, and
%
%\begin{equation}
%  \Gamma_k = 1.
%\label{eq:Gamma_perfect}
%\end{equation}
%
%To see this, we note that
the bin index $i$ is an independent random variable
at each time step $t$, and
%
\begin{align}
  \left\langle
    \xi_i(t) \, \xi_j(t')
  \right\rangle
  %&=
  %\left\langle
  %  \left(
  %    \frac{ h_i(t) } { p_i }
  %    -
  %    \sum_{ r = 1 }^n
  %      \rho_r \frac{ h_r(t) } { p_r }
  %  \right)
  %\right.
  %\notag \\
  %&\hphantom{==}\cdot
  %\left.
  %  \left(
  %    \frac{ h_j(t') } { p_i }
  %    -
  %    \sum_{ s = 1 }^n
  %      \rho_s \frac{ h_s(t') } { p_s }
  %  \right)
  %\right\rangle
  %\notag
  %\\
  &=
  \left(
    \frac{ \delta_{ij} } { p_i }
    -
    \frac{ \rho_i } { p_i }
    -
    \frac{ \rho_j } { p_j }
    +
    \sum_{r = 1}^n
    \frac{ \rho_r^2 } { p_r }
  \right) \,
  \delta_{t, t'}
  ,
\label{eq:zz_perfect}
\end{align}
%
where
we have assumed the asymptotic limit
such that $\langle h_i(t) \rangle = p_i$,
which leads to,
by Eqs. \eqref{eq:h_split} and \eqref{eq:xi_def},
$$
  \xi_i(t)
  =
  \frac{ h_i(t) } { p_i }
  -
  \sum_{ r = 1 }^n
    \rho_r \frac{ h_r(t) } { p_r }
  .
$$
%$\delta(t - t')$ is the equivalent of $\delta_{t, t'}$
%in the continuous limit.
%
\note{To show Eq. \eqref{eq:zz_perfect}, we first note that
  with $t \ne t'$ (going back to the discrete time case),
  $$
  \begin{aligned}
  \left\langle
    \xi_i(t) \, \xi_j(t')
  \right\rangle
  &=
  \left\langle
    \xi_i(t)
  \right\rangle
  \left\langle
    \xi_j(t')
  \right\rangle
  =
  0.
  \end{aligned}
  $$
  Next, for $t = t'$, we have
  $$
  \langle
    h_i(t) \, h_j(t)
  \rangle
  = \delta_{ij} \, p_i
  ,
  $$
  which leads to Eq. \eqref{eq:zz_perfect}.
}
%
Thus,
for $k \ge 2$, we get
%
\begin{equation}
  \kappa_k(t - t')
  =
  \sum_{i,j = 1}^n
  \phi_{ki} \phi_{kj}
  \langle \xi_i(t) \, \xi_j(t') \rangle
  %
  =
  \sum_{i = 1}^n \frac{ \phi_{ki}^2 } { p_i }
  \, \delta_{t, t'},
\notag
%\label{eq:kappa_perfect}
\end{equation}
%
where we have used
Eqs. \eqref{eq:ortho1},
\eqref{eq:eta_def},
and
\eqref{eq:zz_perfect}.
%
\note{Proof.%Eq. \eqref{eq:kappa_perfect},
  $$
  \begin{aligned}
  \kappa_k(t - t')
  &=
  \sum_{i,j = 1}^n
  \phi_{ki}
  \phi_{kj}
  \langle \xi_i(t) \, \xi_j(t') \rangle
  \\
  %
  &=
  \sum_{i,j = 1}^n
  \phi_{ki}
  \phi_{kj}
  \left(
    \frac{ \delta_{ij} } { p_i }
    -
    \frac{ \rho_i } { p_i }
    -
    \frac{ \rho_j } { p_j }
    +
    \sum_{r = 1}^n
    \frac{ \rho_r^2 } { p_r }
  \right) \,
  \, \delta_{t, t'}
  .
  \end{aligned}
  $$
  where,
  we have used
  Eq. \eqref{eq:eta_def}
  on the first line,
  %
  Eq. \eqref{eq:zz_perfect}
  on the second line.
  %
  With Eq. \eqref{eq:ortho1},
  only the first term in the parentheses survives.
}
Particularly, if $p_i = \rho_i$, then, by
Eq. \eqref{eq:eig_orthonormal_rows}
$$
\kappa_k(t - t') = 1.
$$
Thus, Eq. \eqref{eq:kappa_delta} is exact,
with
$$
\Gamma_k
=
\sum_{ i = 1}^n \frac{ \phi_{ki}^2 } { p_i },
$$
or if $\mathbf p = \pmb \rho$,
\begin{equation}
  \Gamma_k = 1
  .
\label{eq:Gamma_perfect}
\end{equation}

@@

We can rewrite the error as
a sum of the eigenmode as
%
\begin{align}
  E
  =
  \sum_{ k = 2 }^n
    \left\langle
      \Theta_k^2
    \right\rangle
  ,
\notag
%\label{eq:error_sbin_equil}
\end{align}
%
where
%
$
  \Theta_k
  =
  \frac{ 1 } { T }
  \sum_{ t = 1 } ^ T
    \theta_k( t )
  ,
$
%
with $\theta_k(t)$ defined by Eq. \eqref{eq:eta_def}.
%and $\phi_{k i}$ by Eq. \eqref{eq:eig_orthonormal_cols}.
%\begin{align}
%\theta_k( t )
%=
%\sum_{ i = 1 }^ n
%\phi_{k i} \left[
%             \frac{ h_i(t) }
%                  { p_i    }
%             - 1
%           \right],
%\end{align}
%and
%\begin{align}
%\sum_{ k = 1 }^n
%  \phi_{k i} \, \phi_{k j}
%  = p_i \, \delta_{i j}.
%\end{align}
%
\note{Because
%
\begin{align*}
  \sum_{ k = 1 }^n
    \Theta_k^2
  &=
  \frac{ 1 } { T^2 }
  \sum_{ t, t' = 1 }^T
    \sum_{ k = 1 }^n
      \theta_k( t ) \, \theta_k( t' )
  \\
  &=
  \frac{ 1 } { T^2 }
  \sum_{ t, t' = 1 }^T
    \sum_{ i, j = 1 }^n
      \xi_i(t) \, \xi_j(t')
      %\left[
      %  \frac{ h_i(t) }
      %       { p_i    }
      %  - 1
      %\right]
      %\left[
      %  \frac{ h_j(t') }
      %       { p_j     }
      %  - 1
      %\right]
      \sum_{ k = 1 }^n
        \phi_{k \, i} \, \phi_{k \, j}
  \\
  &=
  \frac{ 1 } { T^2 }
  \sum_{ t, t' = 1 }^T
    \sum_{ i, j = 1 }^n
      \xi_i(t) \, \xi_j(t') \,
      \rho_i \, \delta_{i, j}
  \\
  &=
  \sum_{ i = 1 }^n
  \frac{ 1 } { T }
  \sum_{ t = 1 }^T \xi_i(t)
  \;
  \frac{ 1 } { T }
  \sum_{ t' = 1 }^T \xi_i(t')
  \\
  &=
  \sum_{ i = 1 }^n
    \rho_i \,
      \left(
        \frac{ H_i }
             { p_i }
        -
        \sum_{r = 1}^n \rho_r
        \frac{ H_r }
             { p_r }
      \right)^2
  ,
\end{align*}
where we have used
$$
  \frac{1}{T}
  \sum_{t = 1}^T \xi_i(t)
  =
  \frac{ H_i }
       { p_i }
  -
  \sum_{r = 1}^n \rho_r
  \frac{ H_r }
       { p_r }
  .
$$
}%
The sum starts from $k = 2$, for
by Eq. \eqref{eq:eigenmode1}, % we have
$$
\theta_1(t)
=
\sum_{ i = 1 }^n
  \phi_{1i} \, \left(
    \frac{ h_i(t) } { p_i }
    -
    \sum_{r = 1}^n
    \rho_r
    \frac{ h_r(t) } { p_r }
  \right)
= 0.
$$

In the long-time limit,
\begin{align*}
  \left\langle
    \Theta_k^2
  \right\rangle
  &=
  \frac{1}{T^2}
  \sum_{ t, t' = 1 }^T
  \langle \theta_k(t) \, \theta_k(t') \rangle
  %\\
  %&\approx
  %\frac{1}{T}
  %\sum_{ \tau = -\infty }^{ \infty }
  %\langle \theta_k(t) \, \theta_k(t + \tau) \rangle
  %\\
  %&=
  =
  \frac{1}{T}
  \sum_{\tau = -\infty}^\infty
    \kappa_n(\tau)
  =
  \frac{ \Gamma_k }{ T }
.
\end{align*}
%
Thus,
\begin{equation}
  E
  =
  \frac{ 1 } { T }
  \sum_{ k = 2 }^n \Gamma_k
  .
\label{eq:error_equil}
\end{equation}

@@

>>>>

\documentclass[preprint, floatfix]{revtex4-1}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{upgreek}
\usepackage[table,usenames,dvipsnames]{xcolor}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{hyperref}
\usepackage{setspace}

@@

\definecolor{DarkBlue}{RGB}{0,0,64}
\definecolor{DarkBrown}{RGB}{64,20,10}
\definecolor{DarkGreen}{RGB}{0,64,0}
\definecolor{DarkPurple}{RGB}{64,0,42}
\definecolor{LightGray}{gray}{0.85}
% annotation macros
\newcommand{\repl}[2]{{\color{gray} [#1] }{\color{blue} #2}}
\newcommand{\add}[1]{{\color{blue} #1}}
\newcommand{\del}[1]{{\color{gray} [#1]}}
\newcommand{\note}[1]{{\color{DarkGreen}\footnotesize \textsc{Note.} #1}}
\newcommand{\answer}[1]{{\color{DarkBlue}\footnotesize \textsc{Answer.} #1}}
\newcommand{\summary}[1]{{\color{DarkPurple}\footnotesize \textsc{Summary.} #1}}

@@

Diagonalizing the matrix $\mathbf w$
using the eigenvectors defined in Eqs.
\eqref{eq:eig_w}-\eqref{eq:eig_orthonormal_rows},
we get a set of decoupled equations
%
\begin{equation}
  \dot y_k(t)
  =
  -\alpha(t) \, \lambda_k \, [y_k(t) - \theta_k(t)],
\label{eq:yt_diffeq}
\end{equation}
%
where
\begin{align}
  y_k(t)
  &=
  \sum_{j=1}^n
    \phi_{kj} \, x_j(t)
  ,
  \label{eq:y_def}
  \\
  \theta_k(t)
  &=
  \sum_{j=1}^n
    \phi_{kj} \, \xi_j(t)
  .
  \label{eq:theta_def}
\end{align}

@@

\begin{figure}[h]
\begin{center}
  \makebox[\linewidth][c]{
    \includegraphics[angle=0, width=1.0\linewidth]{fig/erriascan.pdf}
  }
  \caption{
    \label{fig:erriascan}
    Relative error
    versus the initial updating magnitude, $\alpha(0)$,
    for optimal schedules with different $q(T)$.
    Assuming the Gaussian updating scheme
    with $\sigma = 10$,
    and $\alpha_0 = 10^{-4}$.
    %
    The points were obtained from averaging results
    from over 10000 independent simulations;
    the curves are theoretical predictions.
    %
    \note{This figure was produced by
      \texttt{doc/fig/erriascan.gp}.
      The data were saved under
      \texttt{data/iascan}.
    }%
  }
\end{center}
\end{figure}

@@

First, if the sampling is perfect,
%Eq. \eqref{eq:kappa_delta} is exact, and
%
%\begin{equation}
%  \Gamma_k = 1.
%\label{eq:Gamma_perfect}
%\end{equation}
%
%To see this, we note that
the bin index $i$ is an independent random variable
at each time step $t$, and
%
\begin{align}
  \left\langle
    \xi_i(t) \, \xi_j(t')
  \right\rangle
  %&=
  %\left\langle
  %  \left(
  %    \frac{ h_i(t) } { p_i }
  %    -
  %    \sum_{ r = 1 }^n
  %      \rho_r \frac{ h_r(t) } { p_r }
  %  \right)
  %\right.
  %\notag \\
  %&\hphantom{==}\cdot
  %\left.
  %  \left(
  %    \frac{ h_j(t') } { p_i }
  %    -
  %    \sum_{ s = 1 }^n
  %      \rho_s \frac{ h_s(t') } { p_s }
  %  \right)
  %\right\rangle
  %\notag
  %\\
  &=
  \left(
    \frac{ \delta_{ij} } { p_i }
    -
    \frac{ \rho_i } { p_i }
    -
    \frac{ \rho_j } { p_j }
    +
    \sum_{r = 1}^n
    \frac{ \rho_r^2 } { p_r }
  \right) \,
  \delta_{t, t'}
  ,
\label{eq:zz_perfect}
\end{align}
%
where
we have assumed the asymptotic limit
such that $\langle h_i(t) \rangle = p_i$,
which leads to,
by Eqs. \eqref{eq:h_split} and \eqref{eq:xi_def},
$$
  \xi_i(t)
  =
  \frac{ h_i(t) } { p_i }
  -
  \sum_{ r = 1 }^n
    \rho_r \frac{ h_r(t) } { p_r }
  .
$$
%$\delta(t - t')$ is the equivalent of $\delta_{t, t'}$
%in the continuous limit.
%
\note{To show Eq. \eqref{eq:zz_perfect}, we first note that
  with $t \ne t'$ (going back to the discrete time case),
  $$
  \begin{aligned}
  \left\langle
    \xi_i(t) \, \xi_j(t')
  \right\rangle
  &=
  \left\langle
    \xi_i(t)
  \right\rangle
  \left\langle
    \xi_j(t')
  \right\rangle
  =
  0.
  \end{aligned}
  $$
  Next, for $t = t'$, we have
  $$
  \langle
    h_i(t) \, h_j(t)
  \rangle
  = \delta_{ij} \, p_i
  ,
  $$
  which leads to Eq. \eqref{eq:zz_perfect}.
}
%
Thus,
for $k \ge 2$, we get
%
\begin{equation}
  \kappa_k(t - t')
  =
  \sum_{i,j = 1}^n
  \phi_{ki} \phi_{kj}
  \langle \xi_i(t) \, \xi_j(t') \rangle
  %
  =
  \sum_{i = 1}^n \frac{ \phi_{ki}^2 } { p_i }
  \, \delta_{t, t'},
\notag
%\label{eq:kappa_perfect}
\end{equation}
%
where we have used
Eqs. \eqref{eq:ortho1},
\eqref{eq:theta_def},
and
\eqref{eq:zz_perfect}.
%
\note{Proof.%Eq. \eqref{eq:kappa_perfect},
  $$
  \begin{aligned}
  \kappa_k(t - t')
  &=
  \sum_{i,j = 1}^n
  \phi_{ki}
  \phi_{kj}
  \langle \xi_i(t) \, \xi_j(t') \rangle
  \\
  %
  &=
  \sum_{i,j = 1}^n
  \phi_{ki}
  \phi_{kj}
  \left(
    \frac{ \delta_{ij} } { p_i }
    -
    \frac{ \rho_i } { p_i }
    -
    \frac{ \rho_j } { p_j }
    +
    \sum_{r = 1}^n
    \frac{ \rho_r^2 } { p_r }
  \right) \,
  \, \delta_{t, t'}
  .
  \end{aligned}
  $$
  where,
  we have used
  Eq. \eqref{eq:theta_def}
  on the first line,
  %
  Eq. \eqref{eq:zz_perfect}
  on the second line.
  %
  With Eq. \eqref{eq:ortho1},
  only the first term in the parentheses survives.
}
Particularly, if $p_i = \rho_i$, then, by
Eq. \eqref{eq:eig_orthonormal_rows}
$$
\kappa_k(t - t') = 1.
$$
Thus, Eq. \eqref{eq:kappa_delta} is exact,
with
$$
\Gamma_k
=
\sum_{ i = 1}^n \frac{ \phi_{ki}^2 } { p_i },
$$
or if $\mathbf p = \pmb \rho$,
\begin{equation}
  \Gamma_k = 1
  .
\label{eq:Gamma_perfect}
\end{equation}

@@

We can rewrite the error as
a sum of the eigenmode as
%
\begin{align}
  E
  =
  \sum_{ k = 2 }^n
    \left\langle
      \Theta_k^2
    \right\rangle
  ,
\notag
%\label{eq:error_sbin_equil}
\end{align}
%
where
%
$
  \Theta_k
  =
  \frac{ 1 } { T }
  \sum_{ t = 1 } ^ T
    \theta_k( t )
  ,
$
%
with $\theta_k(t)$ defined by Eq. \eqref{eq:theta_def}.
%and $\phi_{k i}$ by Eq. \eqref{eq:eig_orthonormal_cols}.
%\begin{align}
%\theta_k( t )
%=
%\sum_{ i = 1 }^ n
%\phi_{k i} \left[
%             \frac{ h_i(t) }
%                  { p_i    }
%             - 1
%           \right],
%\end{align}
%and
%\begin{align}
%\sum_{ k = 1 }^n
%  \phi_{k i} \, \phi_{k j}
%  = p_i \, \delta_{i j}.
%\end{align}
%
\note{Because
%
\begin{align*}
  \sum_{ k = 1 }^n
    \Theta_k^2
  &=
  \frac{ 1 } { T^2 }
  \sum_{ t, t' = 1 }^T
    \sum_{ k = 1 }^n
      \theta_k( t ) \, \theta_k( t' )
  \\
  &=
  \frac{ 1 } { T^2 }
  \sum_{ t, t' = 1 }^T
    \sum_{ i, j = 1 }^n
      \xi_i(t) \, \xi_j(t')
      %\left[
      %  \frac{ h_i(t) }
      %       { p_i    }
      %  - 1
      %\right]
      %\left[
      %  \frac{ h_j(t') }
      %       { p_j     }
      %  - 1
      %\right]
      \sum_{ k = 1 }^n
        \phi_{k \, i} \, \phi_{k \, j}
  \\
  &=
  \frac{ 1 } { T^2 }
  \sum_{ t, t' = 1 }^T
    \sum_{ i, j = 1 }^n
      \xi_i(t) \, \xi_j(t') \,
      \rho_i \, \delta_{i, j}
  \\
  &=
  \sum_{ i = 1 }^n
  \frac{ 1 } { T }
  \sum_{ t = 1 }^T \xi_i(t)
  \;
  \frac{ 1 } { T }
  \sum_{ t' = 1 }^T \xi_i(t')
  \\
  &=
  \sum_{ i = 1 }^n
    \rho_i \,
      \left(
        \frac{ H_i }
             { p_i }
        -
        \sum_{r = 1}^n \rho_r
        \frac{ H_r }
             { p_r }
      \right)^2
  ,
\end{align*}
where we have used
$$
  \frac{1}{T}
  \sum_{t = 1}^T \xi_i(t)
  =
  \frac{ H_i }
       { p_i }
  -
  \sum_{r = 1}^n \rho_r
  \frac{ H_r }
       { p_r }
  .
$$
}%
The sum starts from $k = 2$, for
by Eq. \eqref{eq:eigenmode1}, % we have
$$
\theta_1(t)
=
\sum_{ i = 1 }^n
  \phi_{1i} \, \left(
    \frac{ h_i(t) } { p_i }
    -
    \sum_{r = 1}^n
    \rho_r
    \frac{ h_r(t) } { p_r }
  \right)
= 0.
$$

In the long-time limit,
\begin{align*}
  \left\langle
    \Theta_k^2
  \right\rangle
  &=
  \frac{1}{T^2}
  \sum_{ t, t' = 1 }^T
  \langle \theta_k(t) \, \theta_k(t') \rangle
  %\\
  %&\approx
  %\frac{1}{T}
  %\sum_{ \tau = -\infty }^{ \infty }
  %\langle \theta_k(t) \, \theta_k(t + \tau) \rangle
  %\\
  %&=
  =
  \frac{1}{T}
  \sum_{\tau = -\infty}^\infty
    \kappa_k(\tau)
  =
  \frac{ \Gamma_k }{ T }
.
\end{align*}
%
Thus,
\begin{equation}
  E
  =
  \frac{ 1 } { T }
  \sum_{ k = 2 }^n \Gamma_k
  .
\label{eq:error_equil}
\end{equation}

@@

\note{The table of symbols is listed in Table \ref{tab:symbols}.
  \begin{table*}\footnotesize
  \centering
  \rowcolors{1}{white}{LightGray}
  \setlength{\tabcolsep}{4pt} % column separation
  %
  \caption{\label{tab:symbols}Table of symbols.}
  \begin{tabular}{l | p{12cm} }
    Symbol          &   Description \\
    \hline
    $\mathbf{A}$    &   Transition matrix. \\
    $\alpha$        &   Updating magnitude. \\
    $b$             &   Cutoff of the kernel of homogeneous updating schemes. \\
    $C$             &   $C \equiv \int_0^{ q(T) } M(Q) \, dQ$.  \\
    $\delta$        &   Dirac's $\delta$-function. \\
    $c$             &   Constant. \\
    $\Err$          &   Error. \\
    $\ln f$         &   Updating factor in the WL algorithm.  \\
    $\phi_{ki}$     &   Eigenvectors of the updating matrix. \\
    $g$             &   Degeneracy factor, $2$ for a periodic variable, or $1$ a non-periodic one. \\
    $\Gamma_k$      &   Integral of the autocorrelation function of mode $k$. \\
    $h_i(t)$        &   Histogram.  \\
    $H_i$           &   Average histogram.  \\
    $i, j$          &   Bin indices. \\
    $\lambda_k$     &   The $k$th eigenvalue of the updating matrix. \\
    $k, l$          &   Mode indices. \\
    $K$             &   Cutoff wave number of bandpass updating schemes.  \\
    $\kappa_k(t)$   &   Autocorrelation function of mode $k$. \\
    $M(Q)$          &   Mass function, Eq. \eqref{eq:mass_func}.   \\
    $m(Q)$          &   Mass distribution,
                        $m(Q) \equiv M(Q)/\int_0^{ q(T) } M(Q') \, dQ'$.  \\
    $\mu_i$         &   Updating kernel of a homogeneous updating scheme. \\
    $n$             &   Number of bins. \\
    $\nu_k$         &   $\nu_k \equiv \lambda_k / \lambda$. \\
    $p_i$           &   Distribution. \\
    $\pi_i$         &   (Instantaneous) distribution, Eq. \eqref{eq:pi_p_phi} \\
    $q(t)$          &   $\int_0^t \alpha(t') \, dt'$.  \\
    $Q$             &   $q(T) - q(t)$.  \\
    $\theta_k(t)$   &   Noise of mode $k$, Eq. \eqref{eq:theta_def}. \\
    $\rho_i$        &   Distribution used to define the error. \\
    $\sigma_{ij}(t)$   &   Autocorrelation function of $\zeta_i(t)$. \\
    $\sigma$        &   Width of the Gaussian updating scheme. \\
    $t, \tau$       &   Time. \\
    $T$             &   Simulation length. \\
    $u_i(q')$       &   $u_i(q') \equiv e^{\lambda \, [q - q(T)]}$. \\
    $V_i(t)$        &   Original bias potential. \\
    $v_i(t)$        &   Shifted bias potential. \\
    $\mathbf w$     &   Updating matrix. \\
    $x_i(t)$        &   Average-deducted bias potential, Eq. \eqref{eq:x_def}. \\
    $\xi_i(t)$      &   The noise, Eq. \eqref{eq:xi_def}. \\
    $\chi_i$        &   $\chi_i \equiv \ln \frac{ p_i } { p^*_i } - \sum_{ j = 1 }^n p_j \, \ln \frac{ p_j } { p^*_j }$. \\
    $y_k(t)$        &   Mode of the shifted bias potential, Eq. \eqref{eq:y_def}. \\
    $Y_k$           &   Mode of the original bias potential, Eq. \eqref{eq:Y_def}. \\
    $z$             &   Reaction coordinate. \\
    $\zeta_i(t)$    &   The noise part of the instantaneous histogram, $h_i(t)$.
  \end{tabular}
  \end{table*}
}
